Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
adding reference.

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest, and
    extended Haddock's markup to support examples, back in 2010
\item
    We added support for QuickCheck properties to Doctest, and extended
    Haddock's markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Haddock}

>>>>

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest, and
    extended Haddock's markup to support examples, back in 2010
    (Section \ref{sec:haddock} and \ref{sec:doctest})
\item
    We added support for QuickCheck properties to Doctest, and extended
    Haddock's markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Haddock}
\label{sec:haddock}
